---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readosense

<!-- badges: start -->
<!-- badges: end -->

The readosense R package provides an easy way to import raw files from Eosense ecosystem gas flux chambers as R objects that can be used with the [Fluxible](https://plant-functional-trait-course.github.io/fluxible/) package.

## Installation

You can install the development version of readosense from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jogaudard/reosense")
```

## Workflow

### Importing the log files
```{r imports}
library(readosense)

# this step is not needed if you know where your data are
path_logs <- system.file("extdata/ex_logs", package = "readosense")

logs <- eo_import_logs(path_logs)

chamber_log <- eo_logs(logs)

env_variables <- eo_env(logs)
```
Doing so, the function `eo_import_logs` is run only once, which is faster.

### Importing the data files

```{r data}

# this step is not needed if you know where your data are
path_data <- system.file("extdata/ex_data", package = "readosense")

data <- eo_data(path_data)


# it is more practical to join the environmental data here

library(dplyr)

data <- data |>
  left_join(env_variables, by = join_by(f_datetime == datetime))

```

### Using fluxible

The first step of the fluxible workflow would look like this:
```{r fluxible}
library(fluxible)

conc <- flux_match(
    raw_conc = data,
    field_record = chamber_log,
    f_datetime = f_datetime,
    start_col = closing,
    end_col = opening,
    fixed_length = FALSE
)

# View(conc)

```

